---
title: "cluster based on business KPIs"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
Reading data into R.

```{r}
dat2 <- read.csv("full_data.csv", header=T, na.strings=c("","NA"))
```

Counting the number of NAs in dataframe
```{r}
colMeans(is.na(dat2))
```

65% of company variable are na. Let us drop this column.

```{r}
dat2 <- dat2[-10]
```

```{r}
unique(dat2$osp)
unique(dat2$account_type)
```
There is only one level for "osp" variable. Let us drop that as well.

```{r}
dat2 <- dat2[-3]
dat2 <- dat2[-6]
```


## Data Preprocessing

Let us convert balance date variable to real date.
```{r}
dat2$balance_date <- as.Date(dat2$balance_date, format = "%Y-%m-%d")
class(dat2$balance_date)
```

Let us see how many differece currency in our dataframe.

```{r}
unique(dat2$currency)
```

Let us subset by this levels.

```{r}
AUD = as.data.frame(dat2[which(dat2$currency == "AUD"),])
NZD = as.data.frame(dat2[which(dat2$currency == "NZD"),])
USD = as.data.frame(dat2[which(dat2$currency == "USD"),])
GBP = as.data.frame(dat2[which(dat2$currency == "GBP"),])
```

```{r}
usertype <- paste(NZD$user, NZD$account_name, sep = "+")
NZD <- cbind(usertype, NZD)
```


We can see there are too less observatios in AUD, GBP, and USD. So, I am going to fouce on NZD

```{r}
lmp <- function (modelobject) {
    if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
    f <- summary(modelobject)$fstatistic
    p <- pf(f[1],f[2],f[3],lower.tail=F)
    attributes(p) <- NULL
    return(p)
}
```

```{r}
p_value <- c()
drop <- c()
coeff<- c()
daily_profit =  c()
date = c()
user_id = c()
account_id = c()
daily_income = c()
user <- unique(NZD$user)
for (use in user){
  account_name <- unique(NZD[which(NZD$user == use), ]$account_name)
  part <- as.data.frame(NZD[which(NZD$user==use), ])
  part_sum <- aggregate(. ~balance_date, data=part, sum, na.rm=TRUE)
  if (min(part_sum$balance_date) < as.Date("2020-01-01", format = "%Y-%m-%d")){
    part_sum <- part_sum[which((part_sum$balance_date) < as.Date("2020-01-01", format = "%Y-%m-%d")), ]
    #plot.new()
    if(length(part_sum$balance_date) >= 5){
      x <- part_sum$balance_date
      y <- part_sum$NZD
      #plot(x, y)
      coeff <- c(coeff, coef(lm(y~x))[2])
      p_value <- c(p_value, lmp(lm(y~x))) 
    }
    else{
      drop <- c(drop, use)
    }
  }
  else{
      if(length(part_sum$balance_date) >= 5){
      x <- part_sum$balance_date
      y <- part_sum$NZD
      #plot(x, y)
      coeff <- c(coeff, coef(lm(y~x))[2])
      p_value <- c(p_value, lmp(lm(y~x))) 
    }
    else{
      drop <- c(drop, use)
    }
  }
  for (name in account_name){
    #print(length(part[which(part$account_name == name), ]$revenue_to_date))
    user_id <- c(user_id, use)
    account_id <- c(account_id, name)
    
    if (length(part[which(part$account_name == name), ]$revenue_to_date) > 1){
      daily_profit <- c(daily_profit, part[which(part$account_name == name), ]$revenue_to_date[length(part[which(part$account_name == name), ]$revenue_to_date)] - part[which(part$account_name == name), ]$revenue_to_date[1])
      date <- c(date, max(part[which(part$account_name == name),]$balance_date)- min(part[which(part$account_name == name),]$balance_date))
      daily_income <- c(daily_income, mean(part[which(part$account_name == name), ]$NZD[-1]))}
    else{
      daily_profit <- c(daily_profit, part[which(part$account_name == name), ]$revenue_to_date[1])
      date <- c(date, 1)
      daily_income <- c(daily_income, part[which(part$account_name == name), ]$NZD[1])
    }
    #print(NZD[which(NZD$user==use), ][which(account_name == name), ]$revenue_to_date[length(NZD[which(NZD$user==use), ][which(account_name == name), ]$revenue_to_date)]-NZD[which(NZD$user==use), ][which(account_name == name), ]$revenue_to_date[1])
  }
  
}
```

```{r}
profit_day <- as.numeric(daily_profit)/as.numeric(date)
expenses <- as.numeric(daily_income) - as.numeric(profit_day)
new_data <- as.data.frame(cbind(user_id, account_id, daily_profit, date, profit_day, daily_income, expenses))
```

Remove data record with day equal to one.

```{r}
#unique(new_data[which(new_data$date == 1), ]$user_id)
#new_data <- new_data[which(new_data$date != 1), ] ##Question how can we handle those date equal to one?
```

```{r}
dim(new_data)
#plot(new_data$profit_day, new_data$daily_income)
```

Now, we are reducing data from 77898 to 3931.

## Data visulization


```{r}
x <- as.numeric(levels(new_data$profit_day))[new_data$profit_day]
y <- as.numeric(levels(new_data$daily_income))[new_data$daily_income]
plot(round(x), round(y), xlab = "daily profit", ylab = "daily income", main = "Account base daily income VS daily profit")
```

## We can also set the interval in here.

```{r}
#new_data1 <- new_data[which(as.numeric(levels(new_data$profit_day))[new_data$profit_day] <= 200), ]
#new_data1 <- new_data1[which(as.numeric(levels(new_data$profit_day))[new_data$profit_day] >= -200), ]
#new_data1 <- new_data1[which(as.numeric(levels(new_data$daily_income))[new_data$daily_income] <= 1000), ]
#new_data1 <- new_data1[which(as.numeric(levels(new_data$daily_income))[new_data$daily_income] >= -1000), ]
```

```{r}
#x <- as.numeric(levels(new_data1$profit_day))[new_data1$profit_day]
#y <- as.numeric(levels(new_data1$daily_income))[new_data1$daily_income]
#plot(round(x), round(y), xlab = "daily profit", ylab = "daily income", main = "Account base daily income VS daily profit")
```


```{r, warning=FALSE}
x <- as.numeric(levels(new_data$profit_day))[new_data$profit_day]
y <- as.numeric(levels(new_data$expenses))[new_data$expenses]
plot(log(round(x)), log(round(y)), main = "Account base daily expenses VS daily profit", xlab = "daily profit", ylab = "daily expenses")
```

  ```{r, warning = FALSE}
  x <- as.numeric(levels(new_data$daily_income))[new_data$daily_income]
  y <- as.numeric(levels(new_data$expenses))[new_data$expenses]
  plot(log(round(x)), log(round(y)), xlab = "daily income", ylab = "daily expenses", main = "Account base daily expenses VS daily income")
  ```

## Let us just consider company base.

```{r}
profit <- c()
income <- c()
outcome <- c()
company_id <- c()
number_accounts <- c()
companies <- unique(new_data$user_id)
companies <- companies[!companies %in% drop]
for(company in companies){
  company_id <- c(company_id, company)
  profit <- c(profit, sum(as.numeric(levels(new_data[which(new_data$user_id == company), ]$profit_day))[new_data[which(new_data$user_id == company), ]$profit_day]))
  income <- c(income, sum(as.numeric(levels(new_data[which(new_data$user_id == company), ]$daily_income))[new_data[which(new_data$user_id == company), ]$daily_income]))
  outcome <- c(outcome, sum(as.numeric(levels(new_data[which(new_data$user_id == company), ]$expenses))[new_data[which(new_data$user_id == company), ]$expenses]))
  number_accounts <- c(number_accounts, length(new_data[which(new_data$user_id == company),]$account_id))
} 
```



```{r}
business <- as.data.frame(cbind(company_id, profit, income, outcome, number_accounts, coeff, p_value))
```

## Data visulization

```{r, warning=FALSE}
y <- as.numeric(levels(business$profit))[business$profit]
x <- as.numeric(levels(business$income))[business$income]
plot(log(round(x)), log(round(y)), xlab = "log of daily income", ylab = "log of daily profit", main = "log of daily income vs log of daily profit")
```

## Fitting model

```{r, warning=FALSE}
linear_fit <- lm(log(y)~log(x))
summary(linear_fit)
```

## Adding fitted line into graph.

```{r, warning=False}
y <- as.numeric(levels(business$profit))[business$profit]
x <- as.numeric(levels(business$income))[business$income]
plot(log(round(x)), log(round(y)), xlab = "log of daily income", ylab = "log of daily profit", main = "log of daily income vs log of daily profit")
abline(linear_fit, col = "blue")
```

```{r}
x <- as.numeric(levels(business$profit))[business$profit]
y <- as.numeric(levels(business$number_accounts))[business$number_accounts]
plot(log(round(x)), round(y), ylab = "the number of accounts", xlab = "log of the daily profit", main = "number of accounts vs log of the daily profit")
```





```{r, warning=FALSE}
linear_fit2 <- lm(y~log(x))
summary(linear_fit2)
```
```{r}
x <- as.numeric(levels(business$profit))[business$profit]
y <- as.numeric(levels(business$number_accounts))[business$number_accounts]
plot(log(round(x)), round(y), ylab = "the number of accounts", xlab = "log of the daily profit", main = "number of accounts vs log of the daily profit")
abline(linear_fit2, col = "blue")
```



```{r}
x <- as.numeric(levels(business$income))[business$income]
y <- as.numeric(levels(business$number_accounts))[business$number_accounts]
plot(log(round(x)), round(y), ylab = "the number of accounts", xlab = "log of the daily income", main = "number of accounts vs log of the daily income")
```

## Fitting model

```{r, warning=FALSE}
linear_fit3 <- lm(y~log(x))
summary(linear_fit3)
```


```{r}
x <- as.numeric(levels(business$income))[business$income]
y <- as.numeric(levels(business$number_accounts))[business$number_accounts]
plot(log(round(x)), round(y), ylab = "the number of accounts", xlab = "log of the daily income", main = "number of accounts vs log of the daily income")
abline(linear_fit3, col = "blue")
```

## Write new data into csv file.
```{r}
write.csv(new_data,"new_data.csv", row.names = FALSE)
write.csv(business,"business.csv", row.names = FALSE)
```


Fianlly, we finished data preprocessing and baiscly data analysis. Now, we can apply some cluster algorithms to our new data frame. There are only three variable now "daily profit", "daily income", "number of accounts", thus we can drawing a 3D graph to showing our final result.
