---
title: "cluster based on business KPIs"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

## Loading package

```{r}
library(rlist)
library(rvest)
library(xml2)
library(httr)
library(stringr)
```

## Getting table from html page

```{r}
webpage <- "https://siccode.com/page/what-is-an-anzsic-code"
response <- GET(webpage)
table <- html_table(content(response))[2]
df <- as.data.frame(table)
```

```{r}
companies_type <- read.csv("companies.csv", header = TRUE)
companies_type <- companies_type[!(is.na(companies_type$industry) | companies_type$industry==""), ]
companies_type$industry <- as.character(companies_type$industry)
industry <- unique(companies_type$industry)
```

##pre-processing the table

```{r}
for(index in 1:length(df$X3)){
  if(df$X1[index] != ""){
    cur <- df$X1[index]
  }
  else{
    df$X1[index] = cur
  }
}
```

#Pick the key words

```{r}
a_list <- list()
for (element in unique(df$X1)){
  x <- c(gsub("[,()]","",unlist(strsplit(df[df$X1 == element,]$X3, " "))))
  a_list[[element]] <- unique(x[! x%in% c("and", "of", "for", "Services", "Other")])
}
```


```{r}
lst2 <- unique(strsplit(gsub("\\s+", " ", gsub("and|of|Services|Other,", " ", companies_type$industry), " "), " "))
```


```{r}
for (index in 1:length(lst2)){
  print(index)
  for (name in lst2[[index]]){
    for (index1 in 1:length(a_list)){
      if(name %in% a_list[[index1]]){
        print(list.names(a_list)[index1])
        }
      }
    }
  
}
```

```{r}
labels <- c("E", "C", "L", "G", "G", "K", "I", "unknown", "Q", "H", "A", "M", "G", "P", "P", "P", "R", "K", "G", "Q", "S", "G", "E", "L", "C", "H", "R", "F", "P", "A", "K", "I", "D", "J", "B", "unknown", "O")
```

```{r}
for (index2 in 1:length(industry)){
  companies_type[which(companies_type$industry==industry[index2]),]$industry <- rep(labels[index2], length(companies_type[which(companies_type$industry==industry[index2]),]$industry))
}
```

##Reading data into R.

```{r}
dat2 <- read.csv("full_data.csv", header=T, na.strings=c("","NA"))
```

##Adding labels based on business name

```{r}
wired <- c()
for (element in companies_type$user[duplicated(companies_type$user)]){
  print(companies_type$industry[which(companies_type$user == element)])
  if(element %in% unique(dat2$user)){
    wired <- c(wired, element)
    print(element)
  }
}
```

```{r}
nothave <- c()
value <- 0
for (element in unique(dat2$user)){
  if (!element %in% companies_type$user){
    nothave <- c(nothave, element)
    print(element)
  }
  else{
    value <- value + (element %in% companies_type$user)
  }
}
print(length(unique(dat2$user))-value)
```

Five companies are not labeled in our data-set. 

```{r}
Label <- c() 
for (element in unique(dat2$user)){
  if ((!element %in% nothave)&(!element %in% wired)){
    Label <- c(Label, unique(companies_type[which(unique(companies_type)$user == element), ])$industry)
  }
  else if (element %in% wired){
    if(length(unique(companies_type[which(unique(companies_type)$user == element), ])$industry)==1){
      Label <- c(Label, unique(companies_type[which(unique(companies_type)$user == element), ])$industry)
    }
    else{
      tt <- table(unique(companies_type[which(unique(companies_type)$user == element), ])$industry)
      Label <- c(Label, names(tt[which.max(tt)]))
    }
  }
  else{
    Label <- c(Label, "unknown")
  }
  
}
length(Label)
length(unique(dat2$user))
```

```{r}
Labels <- c()
for (index in 1:length(unique(dat2$user))){
  Labels <- c(Labels, rep(Label[index], length(dat2[which(dat2$user == unique(dat2$user)[index]), ]$user)))
}
length(dat2$user)
length(Labels)
```
```{r}
table(Labels)
```

```{r}
dat2 <- cbind(dat2, Labels)
dat2$Labels <- as.character(dat2$Labels)
```


Counting the number of NAs in dataframe
```{r}
colMeans(is.na(dat2))
```

65% of company variable are na. Let us drop this column.

```{r}
dat2 <- dat2[-10]
```

```{r}
unique(dat2$osp)
unique(dat2$account_type)
```
There is only one level for "osp" variable. Let us drop that as well.

```{r}
dat2 <- dat2[-3]
dat2 <- dat2[-6]
```


## Data Preprocessing

Let us convert balance date variable to real date.
```{r}
dat2$balance_date <- as.Date(dat2$balance_date, format = "%Y-%m-%d")
class(dat2$balance_date)
```

Let us see how many differece currency in our dataframe.

```{r}
unique(dat2$currency)
```

Let us subset by this levels.

```{r}
AUD = as.data.frame(dat2[which(dat2$currency == "AUD"),])
NZD = as.data.frame(dat2[which(dat2$currency == "NZD"),])
USD = as.data.frame(dat2[which(dat2$currency == "USD"),])
GBP = as.data.frame(dat2[which(dat2$currency == "GBP"),])
```

```{r}
usertype <- paste(NZD$user, NZD$account_name, sep = "+")
NZD <- cbind(usertype, NZD)
```

```{r}
NZD <- NZD[c(-2, -3, -4, -6)]
```

```{r}
dim(NZD)
```

```{r}
lmp <- function (modelobject) {
    if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
    f <- summary(modelobject)$fstatistic
    p <- pf(f[1],f[2],f[3],lower.tail=F)
    attributes(p) <- NULL
    return(p)
}
```

```{r}
daily_profit <- c()
daily_income <- c()
p_value <- c()
user_name <- c()
coeff<- c()
Labels <- c()
for (use in unique(NZD$usertype)){
  part_sum <- as.data.frame(NZD[which(NZD$usertype==use), ])
  #part_sum <- aggregate(. ~balance_date, data=part, sum, na.rm=TRUE)
  if(length(part_sum$balance_date) >= 5){
    x <- part_sum$balance_date
    y <- part_sum$NZD
    #plot(x, y)
    coeff <- c(coeff, coef(lm(y~x))[2])
    p_value <- c(p_value, lmp(lm(y~x)))
    user_name <- c(user_name, use)
    period <- max(x) - min(x)
    daily_profit <- c(daily_profit, (part_sum$revenue_to_date[length(part_sum$revenue_to_date)]-part_sum$revenue_to_date[1])/as.numeric(period))
    daily_income <- c(daily_income, mean(part_sum$daily_revenue))
    Labels <- c(Labels, unique(part_sum$Labels))
  }
}
```

```{r}
expenses <- as.numeric(daily_income) - as.numeric(daily_profit)
new_data <- as.data.frame(cbind(user_name, daily_profit, daily_income, expenses, coeff, p_value, Labels))
```


```{r}
dim(new_data)
```

```{r}
x <- as.numeric(levels(new_data$daily_profit))[new_data$daily_profit]
y <- as.numeric(levels(new_data$daily_income))[new_data$daily_income]
plot(round(x), round(y), xlab = "daily profit", ylab = "daily income", main = "Account base daily income VS daily profit")
```

```{r, warning=FALSE}
x <- as.numeric(levels(new_data$daily_profit))[new_data$daily_profit]
y <- as.numeric(levels(new_data$expenses))[new_data$expenses]
plot(log(round(x)), log(round(y)), main = "Account base daily expenses VS daily profit", xlab = "daily profit", ylab = "daily expenses")
```

```{r, warning = FALSE}
x <- as.numeric(levels(new_data$daily_income))[new_data$daily_income]
y <- as.numeric(levels(new_data$expenses))[new_data$expenses]
plot(log(round(x)), log(round(y)), xlab = "daily income", ylab = "daily expenses", main = "Account base daily expenses VS daily income")
```

```{r, warning=FALSE}
y <- as.numeric(levels(new_data$daily_profit))[new_data$daily_profit]
x <- as.numeric(levels(new_data$daily_income))[new_data$daily_income]
plot(log(round(x)), log(round(y)), xlab = "log of daily income", ylab = "log of daily profit", main = "log of daily income vs log of daily profit")
```

## Fitting model

```{r, warning=FALSE}
linear_fit <- lm(y~x)
summary(linear_fit)
```

## Adding fitted line into graph.

```{r, warning=False}
y <- as.numeric(levels(new_data$daily_profit))[new_data$daily_profit]
x <- as.numeric(levels(new_data$daily_income))[new_data$daily_income]
plot(x, y, xlab = "daily income", ylab = "daily profit", main = "log of daily income vs log of daily profit")
abline(linear_fit, col = "blue")
```

## Write new data into csv file.
```{r}
write.csv(new_data,"sub_new_data1.csv", row.names = FALSE)
```



