---
title: "cluster based on business KPIs"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

##Reading data into R.

```{r}
dat2 <- read.csv("full_data.csv", header=T, na.strings=c("","NA"))
```

Counting the number of NAs in dataframe
```{r}
colMeans(is.na(dat2))
```

65% of company variable are na. Let us drop this column.

```{r}
dat2 <- dat2[-10]
```

```{r}
unique(dat2$osp)
unique(dat2$account_type)
```
There is only one level for "osp" variable. Let us drop that as well.

```{r}
dat2 <- dat2[-3]
dat2 <- dat2[-6]
```


## Data Preprocessing

Let us convert balance date variable to real date.
```{r}
dat2$balance_date <- as.Date(dat2$balance_date, format = "%Y-%m-%d")
class(dat2$balance_date)
```

Let us see how many differece currency in our dataframe.

```{r}
unique(dat2$currency)
```

Let us subset by this levels.

```{r}
AUD = as.data.frame(dat2[which(dat2$currency == "AUD"),])
NZD = as.data.frame(dat2[which(dat2$currency == "NZD"),])
USD = as.data.frame(dat2[which(dat2$currency == "USD"),])
GBP = as.data.frame(dat2[which(dat2$currency == "GBP"),])
```

```{r}
usertype <- paste(NZD$user, NZD$account_name, sep = "+")
NZD <- cbind(usertype, NZD)
```

```{r}
NZD <- NZD[c(-2, -3, -4, -6)]
```

```{r}
dim(NZD)
```

```{r}
lmp <- function (modelobject) {
    if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
    f <- summary(modelobject)$fstatistic
    p <- pf(f[1],f[2],f[3],lower.tail=F)
    attributes(p) <- NULL
    return(p)
}
```

```{r}
daily_profit <- c()
daily_income <- c()
p_value <- c()
user_name <- c()
coeff<- c()
Labels <- c()
for (use in unique(NZD$usertype)){
  part <- as.data.frame(NZD[which(NZD$usertype==use), ])
  part_sum <- aggregate(. ~balance_date, data=part, sum, na.rm=TRUE)
  if(length(part_sum$balance_date) >= 5){
    x <- part_sum$balance_date
    y <- part_sum$NZD
    #plot(x, y)
    coeff <- c(coeff, coef(lm(y~x))[2])
    p_value <- c(p_value, lmp(lm(y~x)))
    user_name <- c(user_name, use)
    period <- max(x) - min(x)
    daily_profit <- c(daily_profit, (part_sum$revenue_to_date[length(part_sum$revenue_to_date)]-part_sum$revenue_to_date[1])/as.numeric(period))
    daily_income <- c(daily_income, mean(part_sum$daily_revenue))
    Labels <- c(Labels, unique(part_sum$Labels))
  }
}
```

```{r}
expenses <- as.numeric(daily_income) - as.numeric(daily_profit)
new_data <- as.data.frame(cbind(user_name, daily_profit, daily_income, expenses, coeff, p_value, Labels))
```


```{r}
dim(new_data)
```

```{r}
x <- as.numeric(levels(new_data$daily_profit))[new_data$daily_profit]
y <- as.numeric(levels(new_data$daily_income))[new_data$daily_income]
plot(round(x), round(y), xlab = "daily profit", ylab = "daily income", main = "Account base daily income VS daily profit")
```

```{r, warning=FALSE}
x <- as.numeric(levels(new_data$daily_profit))[new_data$daily_profit]
y <- as.numeric(levels(new_data$expenses))[new_data$expenses]
plot(log(round(x)), log(round(y)), main = "Account base daily expenses VS daily profit", xlab = "daily profit", ylab = "daily expenses")
```

```{r, warning = FALSE}
x <- as.numeric(levels(new_data$daily_income))[new_data$daily_income]
y <- as.numeric(levels(new_data$expenses))[new_data$expenses]
plot(log(round(x)), log(round(y)), xlab = "daily income", ylab = "daily expenses", main = "Account base daily expenses VS daily income")
```

```{r, warning=FALSE}
y <- as.numeric(levels(new_data$daily_profit))[new_data$daily_profit]
x <- as.numeric(levels(new_data$daily_income))[new_data$daily_income]
plot(log(round(x)), log(round(y)), xlab = "log of daily income", ylab = "log of daily profit", main = "log of daily income vs log of daily profit")
```

## Fitting model

```{r, warning=FALSE}
linear_fit <- lm(y~x)
summary(linear_fit)
```

## Adding fitted line into graph.

```{r, warning=False}
y <- as.numeric(levels(new_data$daily_profit))[new_data$daily_profit]
x <- as.numeric(levels(new_data$daily_income))[new_data$daily_income]
plot(x, y, xlab = "daily income", ylab = "daily profit", main = "log of daily income vs log of daily profit")
abline(linear_fit, col = "blue")
```

## Write new data into csv file.
```{r}
write.csv(new_data,"new_data1.csv", row.names = FALSE)
```



