---
title: "dynamic time warping"
author: "Xinyu yao"
date: "2021/1/7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Install package
```{r}
library(dtw)
library(lubridate)
library(dtwclust)
library(tidyverse)
library(dplyr)
library(zoo)
library(rlist)
library(rvest)
library(xml2)
library(httr)
library(stringr)
```

##Reading data into R

```{r}
dat2 <- read.csv("full_data.csv", header=T, na.strings=c("","NA"))
```

## Getting table from html page

```{r}
webpage <- "https://siccode.com/page/what-is-an-anzsic-code"
response <- GET(webpage)
table <- html_table(content(response))[2]
df <- as.data.frame(table)
```

```{r}
companies_type <- read.csv("companies.csv", header = TRUE)
companies_type <- companies_type[!(is.na(companies_type$industry) | companies_type$industry==""), ]
companies_type$industry <- as.character(companies_type$industry)
industry <- unique(companies_type$industry)
```

##pre-processing the table

```{r}
for(index in 1:length(df$X3)){
  if(df$X1[index] != ""){
    cur <- df$X1[index]
  }
  else{
    df$X1[index] = cur
  }
}
```

#Pick the key words

```{r}
a_list <- list()
for (element in unique(df$X1)){
  x <- c(gsub("[,()]","",unlist(strsplit(df[df$X1 == element,]$X3, " "))))
  a_list[[element]] <- unique(x[! x%in% c("and", "of", "for", "Services", "Other")])
}
```


```{r}
lst2 <- unique(strsplit(gsub("\\s+", " ", gsub("and|of|Services|Other,", " ", companies_type$industry), " "), " "))
```

```{r}
labels <- c("E", "C", "L", "G", "G", "K", "I", "unknown", "Q", "H", "A", "M", "G", "P", "P", "P", "R", "K", "G", "Q", "S", "G", "E", "L", "C", "H", "R", "F", "P", "A", "K", "I", "D", "J", "B", "unknown", "O")
```

```{r}
for (index2 in 1:length(industry)){
  companies_type[which(companies_type$industry==industry[index2]),]$industry <- rep(labels[index2], length(companies_type[which(companies_type$industry==industry[index2]),]$industry))
}
```


```{r}
wired <- c()
for (element in companies_type$user[duplicated(companies_type$user)]){
  #print(companies_type$industry[which(companies_type$user == element)])
  if(element %in% unique(dat2$user)){
    wired <- c(wired, element)
    #print(element)
  }
}
```

```{r}
nothave <- c()
value <- 0
for (element in unique(dat2$user)){
  if (!element %in% companies_type$user){
    nothave <- c(nothave, element)
    #print(element)
  }
  else{
    value <- value + (element %in% companies_type$user)
  }
}
print(length(unique(dat2$user))-value)
```


```{r}
Label <- c() 
for (element in unique(dat2$user)){
  if ((!element %in% nothave)&(!element %in% wired)){
    Label <- c(Label, unique(companies_type[which(unique(companies_type)$user == element), ])$industry)
  }
  else if (element %in% wired){
    if(length(unique(companies_type[which(unique(companies_type)$user == element), ])$industry)==1){
      Label <- c(Label, unique(companies_type[which(unique(companies_type)$user == element), ])$industry)
    }
    else{
      tt <- table(unique(companies_type[which(unique(companies_type)$user == element), ])$industry)
      Label <- c(Label, names(tt[which.max(tt)]))
    }
  }
  else{
    Label <- c(Label, "unknown")
  }
  
}
length(Label)
length(unique(dat2$user))
```

```{r}
Labels <- c()
for (index in 1:length(unique(dat2$user))){
  Labels <- c(Labels, rep(Label[index], length(dat2[which(dat2$user == unique(dat2$user)[index]), ]$user)))
}
length(dat2$user)
length(Labels)
```


```{r}
dat2 <- cbind(dat2, Labels)
dat2$Labels <- as.character(dat2$Labels)
```



## Data preprocessing

Counting the number of NAs in dataframe
```{r}
colMeans(is.na(dat2))
```

65% of company variable are na. Let us drop this column.

```{r}
dat2 <- dat2[-10]
```

```{r}
unique(dat2$osp)
unique(dat2$account_type)
```
There is only one level for "osp" variable. Let us drop that as well.

```{r}
dat2 <- dat2[,c(-2, -3, -7)]
```


## Data Preprocessing

Let us convert balance date variable to real date.
```{r}
dat2$balance_date <- as.Date(dat2$balance_date, format = "%Y-%m-%d")
class(dat2$balance_date)
```

Let us see how many differece currency in our dataframe.

```{r}
unique(dat2$currency)
```

Let us subset by this levels.

```{r}
AUD = as.data.frame(dat2[which(dat2$currency == "AUD"),])
NZD = as.data.frame(dat2[which(dat2$currency == "NZD"),])
USD = as.data.frame(dat2[which(dat2$currency == "USD"),])
GBP = as.data.frame(dat2[which(dat2$currency == "GBP"),])
```

```{r}
usertype <- paste(NZD$user, NZD$account_name, sep = "+")
NZD <- cbind(usertype, NZD)
```

```{r}
NZD <- NZD[c(-2, -3, -8)]
```

```{r}
dim(NZD)
```

There is not missing values in out data-set.


```{r}
accounts <- unique(NZD$usertype)
length(accounts)
```

## Filter the business with got too less records.

```{r}
names <- c()
min_date <- Sys.Date()
max_date <- as.Date("1982-01-13")
for (account in accounts){
  number <- sum(NZD$usertype == account)
  min_date <- min(min_date, NZD[NZD$usertype == account, ]$balance_date)
  max_date <- max(max_date, NZD[NZD$usertype == account, ]$balance_date)
  if ((number <= 12) & (julian(max_date, min_date)[1] >= 365)){
    names <- c(names, account)
  }
}
```

```{r}
new_data <- NZD
for (element in names){
  new_data <- new_data[new_data$usertype != element, ]
}
```

```{r}
new_accounts <- unique(new_data$usertype)
length(new_accounts)
```

## A example with two plots.

```{r}
date <- new_data[new_data$usertype == new_accounts[1], ]$balance_date
daily_revenue <- new_data[new_data$usertype == new_accounts[1], ]$daily_revenue
a <- cbind(date, daily_revenue)
plot(new_data[new_data$usertype == new_accounts[1], ]$balance_date, 
new_data[new_data$usertype == new_accounts[1], ]$daily_revenue, xlab = "date", ylab = "daily revenue", main = "plot of daily revenue vs date")

```

```{r}
date <- new_data[new_data$usertype == new_accounts[2], ]$balance_date
daily_revenue <- new_data[new_data$usertype == new_accounts[2], ]$daily_revenue
b <- cbind(date, daily_revenue)
plot(new_data[new_data$usertype == new_accounts[2], ]$balance_date, 
new_data[new_data$usertype == new_accounts[2], ]$daily_revenue, xlab = "date", ylab = "daily revenue", main = "plot of daily revenue vs date")
```


From the above plot we can see they are Not the uniform distribution. For example the company may have 10 records in one month but 0 at the reset of this year.


## Aggregate by month and take the time series data.

```{r}
labels <- unique(new_data$Labels)
```


## The table showing the distribution of each label
```{r}
table(new_data$Labels)
barplot(table(new_data$Labels))
```

## K-means clustering with distance measure equal to Dynamic time warping, input as the cloest 18 months (one and half year).

```{r, warning=FALSE}
for (label in labels){
  print(label)
  sub_new_data <- as.data.frame(new_data[which(new_data$Labels == label), ])
  new_accounts <- unique(sub_new_data$usertype)
  series <- list()
  final <- data.frame()
  for (element in new_accounts){
    part <- as.data.frame(sub_new_data[sub_new_data$usertype == element, ])
    part_sum <- part%>%
    mutate(month = format(balance_date, "%m"), year = format(balance_date, "%Y"))%>%
    group_by(month, year) %>%
    summarise_at(c("daily_revenue", "revenue_to_date"), sum) %>%
    as.data.frame()
    part_sum <- cbind(part_sum, rep(element, nrow(part_sum)))
    colnames(part_sum) <- c("month","year", "daily_revenue", "revenue_to_date", "accounts_name")
    series <- c(series, list(part_sum$daily_revenue))
    final <- rbind(final, part_sum)
    }
  numbers <- unique(final$accounts)
  length(numbers)
  Date <- as.Date(as.yearmon(paste(final$year, final$month, sep = "-")))
  final <- cbind(Date, final)
  series1 <- list()
  indexs <- which(unlist(lapply(series, FUN = length)) > 18)
  for (index in 1:length(numbers)){
    if (index %in% indexs){
      part <- as.data.frame(sub_new_data[sub_new_data$usertype == levels(numbers)[index], ])
      #new_data[new_data$usertype == numbers[index], ]
      part_filter <- part %>%  arrange(desc(balance_date)) %>% slice(1:18)
      series1 <- c(series1, list(part_filter$daily_revenue))
    }
    else{
      series1 <- c(series1, series[index])
    }
  }
  if(length(series1) < 20){
    print("Too less sample for clustering")
  }
  else{
    pc <- tsclust(series1,preproc = zscore, type = "partitional", k = 10L, 
              distance = "dtw_basic", centroid = "pam", 
              seed = 3247L, trace = FALSE)
    plot(pc)
    cluster <- tibble(cluster = c(pc@cluster))$cluster
    rev <- sapply(series1, mean)
    sub <- cbind(cluster, rev)
    print(tapply(rev, cluster, mean))
  }
}
```


## Hierarchical clustering with distance measure equal to Dynamic time warping, input as the cloest 18 months for each labels (one and half year).

```{r}
for (label in labels){
  print(label)
  sub_new_data <- as.data.frame(new_data[which(new_data$Labels == label), ])
  new_accounts <- unique(sub_new_data$usertype)
  series <- list()
  final <- data.frame()
  for (element in new_accounts){
    part <- as.data.frame(sub_new_data[sub_new_data$usertype == element, ])
    part_sum <- part%>%
    mutate(month = format(balance_date, "%m"), year = format(balance_date, "%Y"))%>%
    group_by(month, year) %>%
    summarise_at(c("daily_revenue", "revenue_to_date"), sum) %>%
    as.data.frame()
    part_sum <- cbind(part_sum, rep(element, nrow(part_sum)))
    colnames(part_sum) <- c("month","year", "daily_revenue", "revenue_to_date", "accounts_name")
    series <- c(series, list(part_sum$daily_revenue))
    final <- rbind(final, part_sum)
    }
  numbers <- unique(final$accounts)
  length(numbers)
  Date <- as.Date(as.yearmon(paste(final$year, final$month, sep = "-")))
  final <- cbind(Date, final)
  series1 <- list()
  indexs <- which(unlist(lapply(series, FUN = length)) > 18)
  for (index in 1:length(numbers)){
    if (index %in% indexs){
      part <- as.data.frame(sub_new_data[sub_new_data$usertype == levels(numbers)[index], ])
      #new_data[new_data$usertype == numbers[index], ]
      part_filter <- part %>%  arrange(desc(balance_date)) %>% slice(1:18)
      series1 <- c(series1, list(part_filter$daily_revenue))
    }
    else{
      series1 <- c(series1, series[index])
    }
  }
  if(length(series1) < 20){
    print("Too less sample for clustering")
  }
  else{
    hc_sbd <- tsclust(series1, type = "h", k = 10L,preproc = zscore, seed = 3247L, distance = "dtw_basic", centroid = shape_extraction, control = hierarchical_control(method = "average"), trace = FALSE)
    plot(hc_sbd, type = "sc")
    cluster <- tibble(cluster = c(hc_sbd@cluster))$cluster
    rev <- sapply(series1, mean)
    sub <- cbind(cluster, rev)
    print(tapply(rev, cluster, mean))
  }
}
```
