---
title: "dynamic time warping"
author: "Xinyu yao"
date: "2021/1/7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Install package
```{r}
library(dtw)
library(lubridate)
library(dtwclust)
library(tidyverse)
library(dplyr)
library(zoo)
```

## Reading data into R
```{r}
full_data <- read.csv("full_data.csv", header = T)
```

## Droping unseless columns

```{r}
table(full_data$account_type)
```

There are onlt two levels of account type and most of them are the "sales". We can drop this column as well.

```{r}
full_data <- full_data[,c(-2, -10, -3, -7)]
```

## Subset by currency

```{r}
AUD = as.data.frame(full_data[which(full_data$currency == "AUD"),])
NZD = as.data.frame(full_data[which(full_data$currency == "NZD"),])
USD = as.data.frame(full_data[which(full_data$currency == "USD"),])
GBP = as.data.frame(full_data[which(full_data$currency == "GBP"),])
```


## Droping useless columns

```{r}
NZD <- NZD[, c(-2, -7)]
```

## Handing missing values

```{r}
dim(NZD)
```
```{r}
NZD <- na.omit(NZD)
dim(NZD)
```

There is not missing values in out data-set.


## Convert balance_date column to date type.
```{r}
NZD$balance_date <- as.Date(NZD$balance_date, format = "%Y-%m-%d")
```

## Merge account type with the user.

```{r}
usertype <- paste(NZD$user, NZD$account_name, sep = "+")
NZD <- cbind(usertype, NZD)
```

```{r}
accounts <- unique(NZD$usertype)
length(accounts)
```

## Filter the business with got too less records.

```{r}
names <- c()
min_date <- Sys.Date()
max_date <- as.Date("1982-01-13")
for (account in accounts){
  number <- sum(NZD$usertype == account)
  min_date <- min(min_date, NZD[NZD$usertype == account, ]$balance_date)
  max_date <- max(max_date, NZD[NZD$usertype == account, ]$balance_date)
  if ((number <= 12) & (julian(max_date, min_date)[1] >= 365)){
    names <- c(names, account)
  }
}
```

```{r}
new_data <- NZD
for (element in names){
  new_data <- new_data[new_data$usertype != element, ]
}
```

```{r}
new_accounts <- unique(new_data$usertype)
length(new_accounts)
```

## A example with two plots.

```{r}
date <- new_data[new_data$usertype == new_accounts[1], ]$balance_date
daily_revenue <- new_data[new_data$usertype == new_accounts[1], ]$daily_revenue
a <- cbind(date, daily_revenue)
plot(new_data[new_data$usertype == new_accounts[1], ]$balance_date, 
new_data[new_data$usertype == new_accounts[1], ]$daily_revenue, xlab = "date", ylab = "daily revenue", main = "plot of daily revenue vs date")

```

```{r}
date <- new_data[new_data$usertype == new_accounts[2], ]$balance_date
daily_revenue <- new_data[new_data$usertype == new_accounts[2], ]$daily_revenue
b <- cbind(date, daily_revenue)
plot(new_data[new_data$usertype == new_accounts[2], ]$balance_date, 
new_data[new_data$usertype == new_accounts[2], ]$daily_revenue, xlab = "date", ylab = "daily revenue", main = "plot of daily revenue vs date")
```


From the above plot we can see they are Not the uniform distribution. For example the company may have 10 records in one month but 0 at the reset of this year.


## Aggregate by month and take the time series data.

```{r, warning=FALSE}
series <- list()
final <- data.frame()
for (element in new_accounts){
  part <- as.data.frame(new_data[new_data$usertype == element, ])
  part_sum <- part%>%
  mutate(month = format(balance_date, "%m"), year = format(balance_date, "%Y"))%>%
  group_by(month, year) %>%
  summarise_at(c("daily_revenue", "revenue_to_date"), sum) %>%
  as.data.frame()
  part_sum <- cbind(part_sum, rep(element, nrow(part_sum)))
  colnames(part_sum) <- c("month","year", "daily_revenue", "revenue_to_date", "accounts_name")
  series <- c(series, list(part_sum$daily_revenue))
  final <- rbind(final, part_sum)
  }
```

```{r}
numbers <- unique(final$accounts)
length(numbers)
```

```{r}
Date <- as.Date(as.yearmon(paste(final$year, final$month, sep = "-")))
final <- cbind(Date, final)
head(final)
```

## checking the lenght of the time series.
```{r}
mean(unlist(lapply(series, FUN = length)))
```

Most of the company have more than one year's records. To made or result more clearly we are only consider the closest 18 months.

```{r}
series1 <- list()
indexs <- which(unlist(lapply(series, FUN = length)) > 18)
for (index in 1:length(numbers)){
  if (index %in% indexs){
    part <- as.data.frame(new_data[new_data$usertype == levels(numbers)[index], ])
    #new_data[new_data$usertype == numbers[index], ]
    part_filter <- part %>%  arrange(desc(balance_date)) %>% slice(1:18)
    series1 <- c(series1, list(part_filter$daily_revenue))
  }
  else{
    series1 <- c(series1, series[index])
  }
}
```

```{r}
length(series)
length(series1)
```


## Another example two polts
```{r}
date <- final[final$accounts == numbers[1], ]$Date
daily_revenue <- final[final$accounts == numbers[1], ]$daily_revenue
a <- cbind(date, daily_revenue)
plot(date, daily_revenue, xlab = "month", ylab = "daily revenue", main = "plot of daily revenue vs month")
```


```{r}
date <- final[final$accounts == numbers[2], ]$Date
daily_revenue <- final[final$accounts == numbers[2], ]$daily_revenue
b <- cbind(date, daily_revenue)
plot(date, daily_revenue, xlab = "date", ylab = "daily revenue", main = "plot of daily revenue vs date")
```

## Dynamic time warping (partitional clustering)

```{r}
pc <- tsclust(series,preproc = zscore, type = "partitional", k = 18L, 
              distance = "dtw_basic", centroid = "pam", 
              seed = 3247L, trace = TRUE)
```

```{r}
plot(pc)
```

## Hierarchical clustering with dynaimc time warping

```{r}
hc_sbd <- tsclust(series, type = "h", k = 20L,preproc = zscore, seed = 3247L, distance = "dtw_basic", centroid = shape_extraction, control = hierarchical_control(method = "average"), trace = TRUE)
```


```{r}
plot(hc_sbd, type = "sc")
```

## Getting labels

```{r}
cluster <- tibble(cluster = c(hc_sbd@cluster))
length(cluster$cluster)
unique(cluster)
table(cluster$cluster)
```

## 18 months

```{r}
pc1 <- tsclust(series1,preproc = zscore, type = "partitional", k = 18L, 
              distance = "dtw_basic", centroid = "pam", 
              seed = 3247L, trace = TRUE)
```

```{r}
plot(pc1)
```

```{r}
hc_sbd1 <- tsclust(series1, type = "h", k = 18L,preproc = zscore, seed = 3247L, distance = "dtw_basic", centroid = shape_extraction, control = hierarchical_control(method = "average"), trace = TRUE)
```

```{r}
plot(hc_sbd1, type = "sc")
```

## Getting labels

```{r}
cluster <- tibble(cluster = c(hc_sbd1@cluster))
length(cluster$cluster)
unique(cluster)
table(cluster$cluster)
```



```{r}
label <- c()
for (index in seq(1:length(numbers))){
  label <- c(label, rep(cluster$cluster[index], sum(final$accounts == numbers[index])))
}
result <- cbind(final, label)
```

## Combine result to orginal data-set.

```{r}
#strsplit(levels(result$accounts_name), "+", fixed = TRUE)
label <- c()
full_name <- paste(full_data$user, full_data$account_name, sep = "+")
for (element in unique(full_name)){
  if (element %in% numbers){
    label <- c(label, rep(unique(result[final$accounts_name == element, ]$label), sum(full_name == element)))
  }
  else{
    label <- c(label, rep(NA,sum(full_name == element) ))
  }
}
full_data_result <- cbind(full_data, label)
```

## Combine pervious result all together.

```{r}
k_means <- read.csv("new_result2.csv", header = T)
uniqu <- unique(k_means$company_id)
```

```
```{r}
K_means <- c()
Agg <- c()
Min_Batch <- c()
for (element in unique(full_data$user)){
  if(element %in% uniqu){
    K_means <- c(K_means, rep(unique(k_means[k_means$company_id == element, ]$K_means), sum(full_data$user == element)))
    Agg <- c(Agg, rep(unique(k_means[k_means$company_id == element, ]$Agglomerative), sum(full_data$user == element)))
    Min_Batch <- c(Min_Batch, rep(unique(k_means[k_means$company_id == element, ]$Min_Batch), sum(full_data$user == element)))
  }
  else{
    K_means <- c(K_means, rep(NA,sum(full_data$user == element) ))
    Agg <- c(Agg, rep(NA,sum(full_data$user == element) ))
    Min_Batch <- c(Min_Batch, rep(NA,sum(full_data$user == element) ))
  }
}
full_data_result <- cbind(full_data_result, K_means, Agg, Min_Batch)
```
```
```{r}
K_means <- c()
Agg <- c()
Min_Batch <- c()
for (element in unique(paste(full_data$user, full_data$account_name, sep = "+"))){
  if(element %in% uniqu){
    K_means <- c(K_means, rep(unique(k_means[k_means$company_id == element, ]$K_means), sum(paste(full_data$user, full_data$account_name, sep = "+") == element)))
    Agg <- c(Agg, rep(unique(k_means[k_means$company_id == element, ]$Agglomerative), sum(paste(full_data$user, full_data$account_name, sep = "+") == element)))
    Min_Batch <- c(Min_Batch, rep(unique(k_means[k_means$company_id == element, ]$Min_Batch), sum(paste(full_data$user, full_data$account_name, sep = "+") == element)))
  }
  else{
    K_means <- c(K_means, rep(NA,sum(paste(full_data$user, full_data$account_name, sep = "+") == element) ))
    Agg <- c(Agg, rep(NA,sum(paste(full_data$user, full_data$account_name, sep = "+") == element) ))
    Min_Batch <- c(Min_Batch, rep(NA,sum(paste(full_data$user, full_data$account_name, sep = "+") == element) ))
  }
}
full_data_result <- cbind(full_data_result, K_means, Agg, Min_Batch)
```

## Comparing the dynamic time warping result with the agglomerative cluster reslut.

```{r}
table(full_data_result[which(full_data_result$Agg == 0), ]$label)
```

```{r}
table(full_data_result[which(full_data_result$Agg == 1), ]$label)
```

```{r}
table(full_data_result[which(full_data_result$Agg == 2), ]$label)
```

```{r}
table(full_data_result[which(full_data_result$Agg == 3), ]$label)
```

##Finding the common features of the same label.

```{r}
group17 <- result[which(result$label == 17),]
group17
```

```{r}
library(ggplot2)
```

```{r}
ggplot(group17, aes(x=Date, y = daily_revenue))+ geom_point()+ facet_wrap( ~ accounts_name, scales = "free") + geom_line()
```



```
## The average daily revenue for each group.

```{r}
group1 <- result[which(result$label == 17),]
group2 <- result[which(result$label == 2),]
group3 <- result[which(result$label == 3),]
group4 <- result[which(result$label == 4),]
```

```{r}
mean(group1$daily_revenue)
mean(group2$daily_revenue)
mean(group3$daily_revenue)
mean(group4$daily_revenue)

```

## The average revenue to date.

```{r}
mean(group1$revenue_to_date)
mean(group2$revenue_to_date)
mean(group3$revenue_to_date)
mean(group4$revenue_to_date)
```

## The money left in the account.

```{r}
x <- c()
y <- c()
z <- c()
t <- c()
for (business in unique(group1$accounts)){
  x <- c(x, tail(group1$revenue_to_date[which(group1$accounts == business)], n = 1))
}
mean(x)
for (business in unique(group2$accounts)){
  y <- c(y, tail(group1$revenue_to_date[which(group2$accounts == business)], n = 1))
}
mean(y)
for (business in unique(group3$accounts)){
  z <- c(z, tail(group1$revenue_to_date[which(group3$accounts == business)], n = 1))
}
mean(z)
for (business in unique(group4$accounts)){
  t <- c(t, tail(group1$revenue_to_date[which(group4$accounts == business)], n = 1))
}
mean(t)
```